---
title: "p8105_hw1_sp3804"
author: "Shannon (Seonyoung Park) (sp3804)"
date: "9/15/2020"
output: github_document
---

This is my solution to HW1

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

### Creat a data frame with the specified elements.

```{r}
prob1_df = 
  tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c("a","b","c","d","e","f","g","h","i","j"),
  factor_vec = factor(c("low","low","low","mod","mod","mod","high","high","high","high"))
)
```

### Take the mean of each variable in my data frame.
-result: I can take the mean of number but not character nor factor.
```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0)) #mean = 0.6 (?)
mean(pull(prob1_df, char_vec)) #not possible (x numeric)
mean(pull(prob1_df, factor_vec)) #not possible (x numeric)
```


### Let's use as.numeric function
- result: not possible for character nor factor
- Does this help explain what happens when you try to take the mean?: Yes. Since character and factor cannot be changed as numeric value, we cannot calculate the mean of them. 
```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0)) 
as.numeric(pull(prob1_df, char_vec)) 
as.numeric(pull(prob1_df, factor_vec)) 
```
```{r}
#1
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df,samp) 
#2
as.factor(pull(prob1_df, samp_gt_0))*pull(prob1_df,samp)
#3
as.numeric(as.factor(pull(prob1_df, samp_gt_0)))*pull(prob1_df,samp)
```


## Problem 2

```{r}
library(palmerpenguins)
data("penguins", package = "palmerpenguins")
penguins
nrow(penguins) #344 row
ncol(penguins) #8 column

#another way; glimpse
glimpse(penguins)

#mean of flipper_length_mm; except for NA, mean of flipper_length_mm is 200.9 (mm)
mean(pull(penguins, flipper_length_mm), na.rm=TRUE) 

#scatterplot

ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species))+geom_point()+ggtitle("<Penguins' flipper length vs. bill length>")
ggsave("flipper vs.bill_plot.pdf", height =4, width=6)


```

